---
title: "Intersectional Identity and Vaccine Skepticism"
format: 
  dashboard:
    orientation: columns
    nav-buttons: [github]
    github: https://github.com/grace722/portfolio.git
    theme: lux
    output-dir: docs
    css: styles.css
---


```{r}
library(readr)
library(tidyverse)
library(dplyr)
library(RColorBrewer)
library(ggplot2)

anes_2020 <- read_csv("anes_timeseries_2020_csv_20220210.csv",
  na = c("", ". . ."), show_col_types = FALSE)

anes_2024 <- read_csv("anes_timeseries_2024_csv_20250808.csv",
  na = c("", ". . ."), show_col_types = FALSE)


#vax var
anes_2020$vax_hesitant_20 <- anes_2020$V202381
anes_2020$vax_hesitant_20[anes_2020$vax_hesitant_20 < 0] <- NA
anes_2020$vax_hesitant_20[anes_2020$vax_hesitant_20 == 1] <- 0
anes_2020$vax_hesitant_20[anes_2020$vax_hesitant_20 == 3] <- 1
anes_2020$vax_hesitant_20[anes_2020$vax_hesitant_20 == 2] <- 1

anes_2020$vax_hesitant_20 <- factor(anes_2020$vax_hesitant_20,
                            levels = c(0,1),
                            labels = c("Benefits > risks", "Benefits ≤ risks"))

## race var
anes_2020$race_20 <- anes_2020$V201549x - 1
anes_2020$race_20[anes_2020$race_20 < 0] <- NA
anes_2020$race_20 <- factor(anes_2020$race_20,
                            levels = c(0,1,2,3,4,5),
                            labels = c("White non-Hispanic","Black non-Hispanic", "Hispanic","Asian or Native Hawaiian/other Pacific Islander, non-Hispanic alone","Native American/Alaska Native or other race, non-Hispanic alone", "Multiple races, non-Hispanic"))


## binary race var
anes_2020$nonwhite_20 <- anes_2020$V201549x
anes_2020$nonwhite_20[anes_2020$nonwhite_20 < 0] <- NA
anes_2020$nonwhite_20[anes_2020$nonwhite_20 > 1] <- 2

anes_2020$nonwhite_20 <- factor(anes_2020$nonwhite_20,
                                levels = c(1,2),
                                labels = c("White non-Hispanic","Non-White"))

#black var
anes_2020$black <- anes_2020$V201549x
anes_2020$black[anes_2020$black < 0] <- NA
anes_2020$black[anes_2020$black == 2] <- 2
anes_2020$black[anes_2020$black == 1] <- 1
anes_2020$black[anes_2020$black == 3] <- 1
anes_2020$black[anes_2020$black == 4] <- 1
anes_2020$black[anes_2020$black == 5] <- 1
anes_2020$black[anes_2020$black == 6] <- 1


anes_2020$black <- factor(anes_2020$black,
                                levels = c(1,2),
                                labels = c("Not Black","Black"))

#asian var
anes_2020$asian <- anes_2020$V201549x
anes_2020$asian[anes_2020$asian < 0] <- NA
anes_2020$asian[anes_2020$asian == 1] <- 1
anes_2020$asian[anes_2020$asian == 2] <- 1
anes_2020$asian[anes_2020$asian == 3] <- 1
anes_2020$asian[anes_2020$asian == 5] <- 1
anes_2020$asian[anes_2020$asian == 6] <- 1
anes_2020$asian[anes_2020$asian == 4] <- 2

anes_2020$asian <- factor(anes_2020$asian,
                                levels = c(1,2),
                                labels = c("Not Asian","Asian"))

#gender
anes_2020$female_20 <- anes_2020$V201600


anes_2020$female_20[anes_2020$female_20 < 0] <- NA


anes_2020$female_20 <- factor(anes_2020$female_20,
                              levels = c(1,2),
                              labels = c("Male","Female"))

#income var
anes_2020$income_20 <- anes_2020$V201617x - 1
anes_2020$income_20[anes_2020$income_20 < 0] <- NA

anes_2020$income_20 <- factor(anes_2020$income_20,
                           levels = seq(0,21, by = 1),
                           labels = c("Under $9,999", "$10,000-14,999", "$15,000-19,999", "$20,000-24,999", "$25,000-29,999", "$30,000-34,999", "$35,000-39,999", "$40,000-44,999", "$45,000-49,999", "$50,000-59,999", "$60,000-64,999", "$65,000-69,999", "$70,000-74,999", "$75,000-79,999", "$80,000-89,999", "$90,000-99,999", "$100,000-109,999", "$110,000-124,999", "$125,000-149,999", "$150,000-174,999", "$175,000-249,999", "$250,000 or more"))

anes_2020_clean <- anes_2020 |>
  filter(!is.na(vax_hesitant_20),
         !is.na(nonwhite_20),
         !is.na(black),
         !is.na(asian),
         !is.na(female_20),
         !is.na(income_20)
         )

library(ggplot2)

non_white_plot <- ggplot(anes_2020_clean, aes(x = nonwhite_20, fill = vax_hesitant_20)) +
  geom_bar(position = "fill") +
  labs(
    title = "Race and Vaccine Hesitancy",
    y = "%",
    fill = "Race"
  ) +
  theme_minimal() +
  scale_fill_brewer(palette = "Paired")

black_plot <- ggplot(anes_2020_clean, aes(x = black, fill = vax_hesitant_20)) +
  geom_bar(position = "fill") +
  labs(
    title = "Race and Vaccine Hesitancy",
    y = "%",
    fill = "Race"
  ) +
  theme_minimal() +
  scale_fill_brewer(palette = "Paired")

asian_plot <- ggplot(anes_2020_clean, aes(x = asian, fill = vax_hesitant_20)) +
  geom_bar(position = "fill") +
  labs(
    title = "Race and Vaccine Hesitancy",
    y = "%",
    fill = "Race"
  ) +
  theme_minimal() +
  scale_fill_brewer(palette = "Paired")

gender_plot <- ggplot(anes_2020_clean, aes(x = female_20, fill = vax_hesitant_20)) +
  geom_bar(position = "fill") +
  labs(
    title = "Gender and Vaccine Hesitancy",
    y = "%",
    fill = "Sex"
  ) +
  theme_minimal() +
  scale_fill_brewer(palette = "Paired")


# 2024 data 
anes_2024$vax_hesitant_24 <- anes_2024$V242354
anes_2024$vax_hesitant_24[anes_2024$vax_hesitant_24 < 0] <- NA
anes_2024$vax_hesitant_24[anes_2024$vax_hesitant_24 == 1] <- 0
anes_2024$vax_hesitant_24[anes_2024$vax_hesitant_24 == 3] <- 1
anes_2024$vax_hesitant_24[anes_2024$vax_hesitant_24 == 2] <- 1

anes_2024$vax_hesitant_24 <- factor(anes_2024$vax_hesitant_24,
                            levels = c(0,1),
                            labels = c("Benefits > risks", "Benefits ≤ risks"))

anes_2024_clean <- anes_2024 |>
  filter(!is.na(vax_hesitant_24))
```


# Home

### Column {.width = 70%}

**Why did vaccine attitudes change between 2020-2024 for some people, but not others?** <br>

![Source: Clinical Trials Arena](vaccine1.avif){fig-alt="Pfizer Covid-19 Vaccine next to needle" width="400" fig-bottom-margin="0" fig-align="center"}

<h4>The United States has one of the highest rates of vaccine skepticism (Sallam 2021). As of October 2022, about 2.5 years after the initial outbreak broke out in the US, only 68% of Americans had received a full vaccination course, and only ⅓ had received a booster shot. From 2020 to 2024, the percentage of Americans who believed that the health benefits of vaccines did not outweigh the costs increased from 24% to 33% (ANES).</h4>

### Column {.width = 30%}
#### Tables {.tabset}
::: {.card title="Vaccine Attitudes in 2020"}
```{r}
anes_2020_clean <- anes_2020_clean |>
  mutate(vax_group_20 = case_when(
    vax_hesitant_20 == "Benefits > risks" ~ "Benefits > risks",
    vax_hesitant_20 == "Benefits ≤ risks" ~ "Benefits ≤ risks",
    TRUE ~ NA_character_
  )) 

anes_summary_20 <- anes_2020_clean |>
  count(vax_group_20) |>
  mutate(
    fraction = n / sum(n),
    ymax = cumsum(fraction),
    ymin = lag(ymax, default = 0)
  )

ggplot(anes_summary_20, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=vax_group_20)) +
  geom_rect() +
  coord_polar(theta="y") +
  xlim(c(2, 4)) +
  theme_void() +
  labs(
    fill = "Vaccine Attitudes",
    title = "Do health benefits of vaccinations outweigh the risks?"
  ) +
  scale_fill_manual(values = brewer.pal(3, "Blues")[2:3])  + 
  theme(
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(10, 10, 10, 10)
  )
```
:::
::: {.card title="Vaccine Attitudes in 2024"}

```{r}
anes_2024_clean <- anes_2024_clean |>
  mutate(vax_group_24 = case_when(
    vax_hesitant_24 == "Benefits > risks" ~ "Benefits > risks",
    vax_hesitant_24 == "Benefits ≤ risks" ~ "Benefits ≤ risks",
    TRUE ~ NA_character_
  )) 

anes_summary_24 <- anes_2024_clean |>
  count(vax_group_24) |>
  mutate(
    fraction = n / sum(n),
    ymax = cumsum(fraction),
    ymin = lag(ymax, default = 0)
  )

ggplot(anes_summary_24, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=vax_group_24)) +
  geom_rect() +
  coord_polar(theta="y") +
  xlim(c(2, 4)) +
  theme_void() +
  labs(
    fill = "Vaccine Attitudes",
    title = "Do health benefits of vaccinations outweigh the risks?"
  ) +
  scale_fill_manual(values = brewer.pal(3, "Blues")[2:3]) + 
  theme(
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(10, 10, 10, 10)
  )
```
:::


# The Facts

### Column - Importance of Vaccines

**Why are vaccines important?**

An estimated 154 million lives have been saved by vaccinations in the last 50 years (WHO 2024). This trend of decreasing support for vaccinations could have drastic consequences on public health. The longer it takes to control the spread of an illness, the more time it has to mutate, creating mutations of the virus that are possibly more deadly or vaccine-resistant.

**Why look at Intersectionality?**

Discrimination against racial minorities and women is widespread within the medical system, and this discrimination is compounded for women of color. This is a contributing factor to the higher levels of medical mistrust and avoidance of care observed in people of color and women (Campbell et al. 2025, Bazargan et al. 2021, Do et al 2022).



### Column - Tabsets of tables {.tabset height="70%"}

::: {.card title="White & Non-White"}
```{r}
non_white_plot
```
:::

::: {.card title="Black & Non-Black"}
```{r}
black_plot
```
:::

::: {.card title="Asian & Non-Asian"}
```{r}
asian_plot
```
:::

::: {.card title="Female and Male"}
```{r}
gender_plot
```

\*Sex is used here instead of gender because significantly more data was available under the Sex variable, but it should be noted that gender identity could impact outcomes as well.
:::

# Research Design & Results

### Column - Tabsets of tables {.tabset height="70%"}


```{r}
library(ggeffects)
#vax var
anes_2020$vax_hesitant_20 <- anes_2020$V202381
anes_2020$vax_hesitant_20[anes_2020$vax_hesitant_20 < 0] <- NA
anes_2020$vax_hesitant_20[anes_2020$vax_hesitant_20 == 1] <- 0
anes_2020$vax_hesitant_20[anes_2020$vax_hesitant_20 == 3] <- 1

anes_2020$vax_hesitant_20 <- factor(anes_2020$vax_hesitant_20,
                            levels = c(0,1,2),
                            labels = c("Benefits outweigh risks","Benefits and risks are equal","Risks outweight benefits"))
anes_2020$vax_hesitant_20 <- as.numeric(anes_2020$vax_hesitant_20) - 1
## race var
anes_2020$race_20 <- anes_2020$V201549x - 1
anes_2020$race_20[anes_2020$race_20 < 0] <- NA
anes_2020$race_20 <- factor(anes_2020$race_20,
                            levels = c(0,1,2,3,4,5),
                            labels = c("White non-Hispanic","Black non-Hispanic", "Hispanic","Asian or Native Hawaiian/other Pacific Islander, non-Hispanic alone","Native American/Alaska Native or other race, non-Hispanic alone", "Multiple races, non-Hispanic"))


## binary race var
anes_2020$race_20 <- as.numeric(anes_2020$race_20) - 1


anes_2020$nonwhite_20 <- anes_2020$race_20
anes_2020$nonwhite_20[anes_2020$race_20 > 0] <- 1

anes_2020$nonwhite_20 <- factor(anes_2020$nonwhite_20,
                                levels = c(0,1),
                                labels = c("White non-Hispanic","Non-White"))


anes_2020$nonwhite_20 <- as.numeric(anes_2020$nonwhite_20) - 1

#black var
anes_2020$black <- anes_2020$race_20
anes_2020$black[anes_2020$race_20 > 1] <- 0


#asian var
anes_2020$asian <- anes_2020$race_20
anes_2020$asian[anes_2020$race_20 < 3] <- 0
anes_2020$asian[anes_2020$race_20 == 3] <- 1
anes_2020$asian[anes_2020$race_20 > 3] <- 0


## gender var

anes_2020$female_20 <- anes_2020$V201600 - 1


anes_2020$female_20[anes_2020$female_20 < 0] <- NA


anes_2020$female_20 <- factor(anes_2020$female_20,
                           levels = c(0,1),
                           labels = c("Male","Female"))

anes_2020$female_20 <- as.numeric(anes_2020$female_20) - 1



##income var
anes_2020$income_20 <- anes_2020$V201617x - 1
anes_2020$income_20[anes_2020$income_20 < 0] <- NA

anes_2020$income_20 <- factor(anes_2020$income_20,
                           levels = seq(0,21, by = 1),
                           labels = c("Under $9,999", "$10,000-14,999", "$15,000-19,999", "$20,000-24,999", "$25,000-29,999", "$30,000-34,999", "$35,000-39,999", "$40,000-44,999", "$45,000-49,999", "$50,000-59,999", "$60,000-64,999", "$65,000-69,999", "$70,000-74,999", "$75,000-79,999", "$80,000-89,999", "$90,000-99,999", "$100,000-109,999", "$110,000-124,999", "$125,000-149,999", "$150,000-174,999", "$175,000-249,999", "$250,000 or more"))
anes_2020$income_20 <- as.numeric(anes_2020$income_20) - 1



## education var
anes_2020$edu_20 <- anes_2020$V201511x - 1
anes_2020$edu_20[anes_2020$edu_20 < 0] <- NA

anes_2020$edu_20 <- factor(anes_2020$edu_20,
                           levels = seq(0,4, by = 1),
                           labels = c("Less than high school credential", "High school credential", "Some post-high school, no bachelor’s degree", "Bachelor’s degree", "Graduate degree"))

anes_2020$edu_20 <- as.numeric(anes_2020$edu_20) - 1

## conspiracy var
anes_2020$conspiracy_20 <- anes_2020$V202312 - 1
anes_2020$conspiracy_20[anes_2020$conspiracy_20 < 0] <- NA

##party id
anes_2020$republican <- anes_2020$V201231x - 1
anes_2020$republican[anes_2020$republican < 0] <- NA
anes_2020$republican <- factor(anes_2020$republican,
                           levels = seq(0,6, by = 1),
                           labels = c("Strong Democrat", "Not Very Strong Democrat", "Independent-Democrat", "Independent", "Independent-Republican", "Not Very Strong Republican", "Strong Republican"))
anes_2020$republican <- as.numeric(anes_2020$republican) - 1



##fox:
fox_news_programs <- c(anes_2020$V201630b,anes_2020$V201630c,anes_2020$V201630f,anes_2020$V201630g,anes_2020$V201630h,anes_2020$V201630k,anes_2020$V201631k)


anes_2020 <- anes_2020 |>
  mutate(fox = case_when(
     (V201630b < 0 | V201630c < 0 | V201630f < 0 | V201630g < 0 | V201630h < 0 | V201630k < 0 | V201631k < 0) ~ NA,
    (V201630b == 0 & V201630c == 0 & V201630f == 0 & V201630g == 0 & V201630h == 0 & V201630k == 0 & V201631k == 0) ~ 0,
    TRUE ~ 1
  ))


model1 <- lm(vax_hesitant_20 ~ female_20 + nonwhite_20 + (female_20*nonwhite_20) + income_20 + edu_20 + conspiracy_20 + republican + fox, data = anes_2020)

model2 <- lm(vax_hesitant_20 ~ female_20 + black + (female_20*black) + income_20 + edu_20 + conspiracy_20 + republican + fox + asian + (female_20*asian), data = anes_2020)
```

::: {.card title="Female & Non-white"}
```{r}
pred1_nonw <- ggpredict(model1, terms = c("female_20", "nonwhite_20"))
plot(pred1_nonw) + labs(
  x = "Female",
  y = "Vaccine Hesitancy",
  title = "Effect of Intersectional Identity (Race and Gender) on Vaccine Hesitancy",
  color = "Race") + 
  scale_color_manual(
    values = c("royalblue3", "mediumpurple1"),
    labels = c("Non-white", "White")
  ) +
  scale_fill_manual(
    values = c("lightskyblue", "thistle") 
  ) +
  theme_classic() +
  guides(
    color = guide_legend(
      override.aes = list(
        color = c("royalblue3", "mediumpurple1"),
        fill = c("lightskyblue", "thistle")
      )
    )
  )

```
:::

::: {.card title="Female and Black"}
```{r}
pred1 <- ggpredict(model2, terms = c("female_20", "black"))
plot(pred1) + labs(
  x = "Female",
  y = "Vaccine Hesitancy",
  title = "Effect of Intersectional Identity (Race and Gender) on Vaccine Hesitancy",
  color = "Race") + 
  scale_color_manual(
    values = c("royalblue3", "mediumpurple1"),
    labels = c("Not Black", "Black")
  ) +
  scale_fill_manual(
    values = c("lightskyblue", "thistle") 
  ) +
  theme_classic() +
  guides(
    color = guide_legend(
      override.aes = list(
        color = c("royalblue3", "mediumpurple1"),
        fill = c("lightskyblue", "thistle")
      )
    )
  )
```
:::

::: {.card title="Female and Asian"}
```{r}
pred2 <- ggpredict(model2, terms = c("female_20", "asian"))

plot(pred2) +
  labs(
    x = "Female",
    y = "Vaccine Hesitancy",
    title = "Effect of Intersectional Identity (Race and Gender) on Vaccine Hesitancy",
    color = "Race"
  ) +
  scale_color_manual(
    values = c("royalblue3", "mediumpurple1"),
    labels = c("Not Asian", "Asian")
  ) +
  scale_fill_manual(
    values = c("lightskyblue", "thistle") 
  ) +
  theme_classic() +
  guides(
    color = guide_legend(
      override.aes = list(
        color = c("royalblue3", "mediumpurple1"),
        fill = c("lightskyblue", "thistle")
      )
    )
  )
```
:::

### Column

## Row - rd

Data: [ANES 2020](https://electionstudies.org/data-center/2020-time-series-study/)

What might cause vaccine hesitance? The literature says:

1.  Race

2.  Conspiratorial Thinking

3.  Party Affiliation

4.  Fox News watcher

5.  Sex

6.  Income

7.  Education

Using an OLS Regression model, my findings indicate that:

1.  Being female has a negative relationship with vaccine hesitancy

2.  Being a person of color has a positive relationship with vaccine hesitancy

3.  The intersectional identity - women of color - has a positive but statistically insignificant relationship with vaccine hesitancy.

In short, this model shows no *significant* effect of an intersectional identity between race and gender. The most important factors to predict vaccine hesitancy are race, education, income, conspiracy beliefs, and party affiliation.

# References

📄 [Download the full version of my paper on the topic](An%20Intersectional%20Analysis%20of%20Increasing%20Vaccine%20Skepticism:%20Women%20of%20Color.pdf)

::: {style="margin-left: 1.5em; text-indent: -1.5em;"}
Al Hamid, A., Beckett, R., Wilson, M., Jalal, Z., Cheema, E., Al-Jumeily Obe, D., Coombs, T., Ralebitso-Senior, K., & Assi, S. (2024). Gender Bias in Diagnosis, Prevention, and Treatment of Cardiovascular Diseases: A Systematic Review. Cureus, 16(2), e54264. https://doi.org/10.7759/cureus.54264

Anderson, K. P., Juliana Menasce Horowitz and Monica. (2020, June 12). Amid Protests, Majorities Across Racial and Ethnic Groups Express Support for the Black Lives Matter Movement. Pew Research Center. https://www.pewresearch.org/social-trends/2020/06/12/amid-protests-majorities-across-racial-and-ethnic-groups-express-support-for-the-black-lives-matter-movement/

American National Election Studies. (2021). ANES 2020 Time Series Study

American National Election Studies. (2025). ANES 2024 Time Series Study

Amlani, S., Kiesel, S., & Butters, R. (2023). Polarization in COVID-19 Vaccine Discussion Networks. American Politics Research, 51(2), 260–273. https://doi.org/10.1177/1532673X221148670

Bass, S. B., Wilson-Genderson, M., Garcia, D. T., Akinkugbe, A. A., & Mosavel, M. (2021). SARS-CoV-2 Vaccine Hesitancy in a Sample of US Adults: Role of Perceived Satisfaction With Health, Access to Healthcare, and Attention to COVID-19 News. Frontiers in Public Health, 9, Article 665724. https://doi.org/10.3389/fpubh.2021.665724

Bazargan, M., Cobb, S., & Assari, S. (2021). Discrimination and Medical Mistrust in a Racially and Ethnically Diverse Sample of California Adults. Annals of Family Medicine, 19(1), 4–15. https://doi.org/10.1370/afm.2632

Benjamins, M. R., & Middleton, M. (2019). Perceived discrimination in medical settings and perceived quality of care: A population-based study in Chicago. PloS One, 14(4), Article 0215976. https://doi.org/10.1371/journal.pone.0215976

Campbell, J. A., Walker, R. J., & Egede, L. E. (2025). Medical Mistrust and Perceived Discrimination as Expressions of Structural Racism: The Need for Focused Research: Medical Mistrust and Perceived Discrimination. Journal of General Internal Medicine : JGIM, 40(11), 2489–2490. https://doi.org/10.1007/s11606-025-09489-4

Choi, Y., & Fox, A. M. (2022). Mistrust in public health institutions is a stronger predictor of vaccine hesitancy and uptake than Trust in Trump. Social Science & Medicine (1982), 314, Article 115440. https://doi.org/10.1016/j.socscimed.2022.115440

Community Relations Service \| 2020 FBI Hate Crimes Statistics. (2021, November 17). https://www.justice.gov/archives/crs/highlights/2020-hate-crimes-statistics

Crenshaw, K. (1991). Mapping the Margins: Intersectionality, Identity Politics, and Violence against Women of Color. Stanford Law Review, 43(6), 1241–1299. https://doi.org/10.2307/1229039

Data USA. (n.d.). United States. https://datausa.io/profile/geo/united-states

Do, Q. A., Yang, J. P., Gaska, K. A., Knopp, K., & Scott, S. B. (2023). Centering Asian American Women's Health: Prevalence of Health Care Discrimination and Associated Health Outcomes. Journal of racial and ethnic health disparities, 10(2), 797–804. https://doi.org/10.1007/s40615-022-01267-w

Dorman, C., Perera, A., Condon, C., Chau, C., Qian, J., Kalk, K., & DiazDeleon, D. (2021). Factors Associated with Willingness to be Vaccinated Against COVID-19 in a Large Convenience Sample. Journal of Community Health, 46(5), 1013–1019. https://doi.org/10.1007/s10900-021-00987-0

Fridman, A., Gershon, R., & Gneezy, A. (2021). COVID-19 and vaccine hesitancy: A longitudinal study. PloS One, 16(4), Article 0250123. https://doi.org/10.1371/journal.pone.0250123

Jennings, W., Valgarðsson, V., McKay, L., Stoker, G., Mello, E., & Baniamin, H. M. (2023). Trust and vaccine hesitancy during the COVID-19 pandemic: A cross-national analysis. Vaccine: X, 14, Article 100299. https://doi.org/10.1016/j.jvacx.2023.100299

Kelly, B. J., Southwell, B. G., McCormack, L. A., Bann, C. M., MacDonald, P. D. M., Frasier, A. M., Bevc, C. A., Brewer, N. T., & Squiers, L. B. (2021). Predictors of willingness to get a COVID-19 vaccine in the U.S. BMC Infectious Diseases, 21(1), Article 338. https://doi.org/10.1186/s12879-021-06023-9

Kim, J., Kim, Y., & Li, Y. (2022). Source of information on COVID‐19 vaccine and vaccine hesitancy among U.S. Medicare beneficiaries. Journal of the American Geriatrics Society (JAGS), 70(3), 677–680. https://doi.org/10.1111/jgs.17619

Maloney, E. K., White, A. J., Samuel, L., Boehm, M., & Bleakley, A. (2024). COVID-19 coverage from six network and cable news sources in the United States: Representation of misinformation, correction, and portrayals of severity. Public understanding of science (Bristol, England), 33(1), 58–72. https://doi.org/10.1177/09636625231179588

Morales, D. X., Beltran, T. F., & Morales, S. A. (2022). Gender, socioeconomic status, and COVID‐19 vaccine hesitancy in the US: An intersectionality approach. Sociology of Health & Illness, 44(6), 953–971. https://doi.org/10.1111/1467-9566.13474

Morgan, K. M., Maglalang, D. D., Monnig, M. A., Ahluwalia, J. S., Avila, J. C., & Sokolovsky, A. W. (2023). Medical Mistrust, Perceived Discrimination, and Race: a Longitudinal Analysis of Predictors of COVID-19 Vaccine Hesitancy in US Adults. Journal of racial and ethnic health disparities, 10(4), 1846–1855. https://doi.org/10.1007/s40615-022-01368-6

Nanaw, J., Sherchan, J. S., Fernandez, J. R., Strassle, P. D., Powell, W., & Forde, A. T. (2024). Racial/ethnic differences in the associations between trust in the U.S. healthcare system and willingness to test for and vaccinate against COVID-19. BMC Public Health, 24(1), Article 1084. https://doi.org/10.1186/s12889-024-18526-6

Nguyen, T. T., Criss, S., Kim, M., De La Cruz, M. M., Thai, N., Merchant, J. S., Hswen, Y., Allen, A. M., Gee, G. C., & Nguyen, Q. C. (2023). Racism During Pregnancy and Birthing: Experiences from Asian and Pacific Islander, Black, Latina, and Middle Eastern Women. Journal of Racial and Ethnic Health Disparities, 10(6), 3007–3017. https://doi.org/10.1007/s40615-022-01475-4

Nguyen, Q. C., Yardi, I., Gutierrez, F. X. M., Mane, H., & Yue, X. (2022). Leveraging 13 million responses to the U.S. COVID-19 Trends and Impact Survey to examine vaccine hesitancy, vaccination, and mask wearing, January 2021-February 2022. BMC Public Health, 22(1), Article 1911. https://doi.org/10.1186/s12889-022-14286-3

Sallam, M. (2021). COVID-19 Vaccine Hesitancy Worldwide: A Concise Systematic Review of Vaccine Acceptance Rates. Vaccines (Basel), 9(2), Article 160. https://doi.org/10.3390/vaccines9020160

Silver, D., Kim, Y., McNeill, E., Piltch-Loeb, R., Wang, V., & Abramson, D. (2022). Association between COVID-19 vaccine hesitancy and trust in the medical profession and public health officials. Preventive Medicine, 164, Article 107311. https://doi.org/10.1016/j.ypmed.2022.107311

Stoler, J., Klofstad, C. A., Enders, A. M., & Uscinski, J. E. (2022). Sociopolitical and psychological correlates of COVID-19 vaccine hesitancy in the United States during summer 2021. Social Science & Medicine (1982), 306, Article 115112. https://doi.org/10.1016/j.socscimed.2022.115112

Thunström, L., Ashworth, M., Finnoff, D., & Newbold, S. C. (2021). Hesitancy Toward a COVID-19 Vaccine. EcoHealth, 18(1), 44–60. https://doi.org/10.1007/s10393-021-01524-0

Washington, A., & Randall, J. (2023). “We’re Not Taken Seriously”: Describing the Experiences of Perceived Discrimination in Medical Settings for Black Women. Journal of Racial and Ethnic Health Disparities, 10(2), 883–891. https://doi.org/10.1007/s40615-022-01276-9

World Health Organization. (2024, April 24). Global immunization efforts have saved at least 154 million lives over the past 50 years. https://www.who.int/news/item/24-04-2024-global-immunization-efforts-have-saved-at-least-154-million-lives-over-the-past-50-years/

Zimmerman, T., Shiroma, K., Fleischmann, K. R., Xie, B., Jia, C., Verma, N., & Lee, M. K. (2023). Misinformation and COVID-19 vaccine hesitancy. Vaccine, 41(1), 136–144. https://doi.org/10.1016/j.vaccine.2022.11.014
:::
